Multi-level modeling with Openflexo/\FML

### 2021-09-27 3-introduction.tex
Updates from Overleaf

\textcolor{red}{Our modeling approach is based on two levels. The meta level (\FML) provides the (linguistic) concepts that are used to define the model level (ontological). The ontological level is used to define the models and meta-models that are needed. \FML allows to define models as first class entities (which we call VirtualModel) and to link them together (by extension). In the \mpc case study, we exploit this possibility to:
\begin{itemize}
    \item Extend and adapt existing models, keeping the previous ones, to meet changing modeling needs,
    \item Align this hierarchy of models with the process of their evolution.
\end{itemize}
This methodological choice allows us to adapt the models and keep track of their evolution each time the needs evolve.}

>>>>

\textcolor{red}{Our modeling approach is based on a language (\FML) which provides the (linguistic) concepts that are used to define  the multi-levels models and meta-models that are needed. \FML allows to define models as first class entities (which we call VirtualModel) and to link them together (by extension). In the \mpc case study, we exploit this possibility to:
\begin{itemize}
    \item Define, extend and adapt models, keeping the history, to meet changing modeling requirements of the case study,
    \item Align this hierarchy of models with their specification evolution.
\end{itemize}
This methodological choice allows us to adapt the models and keep track of their evolution each time the requirements evolve.}
